---
title: "Covid91 vaccine study Final2020"
author: "Arlene Faye Salvador"
date: "October 29, 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode aids to say covid and then remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine.

$H_0$ The Null Hypothesis is that among the target population, the vaccine has no effect on whether one contracts the virus or not.

$H_A$ The Alternative Hypothesis is that is that among the target population, the vaccine has an effect on whether one contracts the virus or not.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

# Graphical Results
# Female Report

```{r}
DataF = filter(FinalData, sex=="gal")
barchartGC(~infected + treatment,data=DataF)
barchartGC(~infected + treatment,data=DataF, type="percent")
```  

It appears that the vaccine has a positive effect on the gals since they are less likely to get Covid-19 if they receive the vaccine.  


```{r}
DataG = filter(FinalData, sex=="guy")
barchartGC(~infected + treatment,data=DataG)
barchartGC(~infected + treatment,data=DataG, type="percent")
```  

It appears that the vaccine has a negative effect on the guys since they are more likely to get Covid-19 if they receive the vaccine.  

# Drug User

```{r}
DrugUser = filter(FinalData,DrugUser=="yes")
barchartGC(~infected + treatment,data=DrugUser)
barchartGC(~infected + treatment,data=DrugUser, type="percent", main="DrugUser")

```  

It appears that the vaccine has a positive effect on DrugUsers since they are less likely to get Covid-19 if they receive the vaccine.  


# LGBTQ

```{r}
DataLGBTQ = filter(FinalData,LGBTQ=="gay")
barchartGC(~infected + treatment,data=DataLGBTQ)
barchartGC(~infected + treatment,data=DataLGBTQ, type="percent", main="LGBTQ")

```  

It appears that the vaccine has a negative effect on gays since they are more likely to get Covid-19 if they receive the vaccine.  

# Numerical Summaries

# Female Report
```{r}
DataF = filter(FinalData,sex=="gal")
table1 <- xtabs(~infected + treatment, data=DataF)
rowPerc(table1)
colPerc(table1)
```
According to gals,

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


```{r}
DataG = filter(FinalData,sex=="guy")
table1 <- xtabs(~infected + treatment, data=DataG)
rowPerc(table1)
colPerc(table1)
```
According to Guys,

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


```{r}
DrugUser = filter(FinalData,DrugUser=="yes")
table1 <- xtabs(~infected + treatment, data=DrugUser)
rowPerc(table1)
colPerc(table1)
```

According to DrugUsers,

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


```{r}
DataLGBTQ = filter(FinalData,LGBTQ=="gay")
table1 <- xtabs(~infected + treatment, data=DataLGBTQ)
rowPerc(table1)
colPerc(table1)
```
According to gays,

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

According to the bar charts and numerical results for females, we can see that females that took the drug are less likely to contract COVID-19. There were only 33.11 women infected with COVID-19 and 50.31 that were not infected with the drug. According to the inferential test, 95.56% of women were not infected which makes the vaccine very effective among the female population. The P-Value: 2.2e-16 is less than 0.05, so we reject the null Hypothesis. The vaccine did have an effect which was positive in the Female population, which led to them not contracting COVID-19.

According to the bar charts and numerical results for males, we can see that males were more likely to contract COVID-19. There were 58.16 of males who took the drug and contracted COVID-19, while 48.54 remained okay. The P-value: 6e-04 is less than 0.05, so we reject the null hypothesis. The vaccine had an effect in males, however it was a negative effect because more males contracted COVID-19 than not.

According to the bar charts and numerical results for Drug Users, we can see that Drug Users were less likely to contract COVID-19. There were 33.33 Drug Users infected with COVID-19 with the drug, and 47.83 who were not infected with COVID-19 with the drug. The P-Value: 5.741e-06 is less than 0.05, so we reject the null hypothesis. The vaccine had an effect which was positive in Drug Users, which led to them not contracting COVID-19.

According to the bar charts and numerical results for LGBTQ, we can see that the LGBTQ community were more likely to contract COVID-19. There were 70.69 who contracted COVID-19 with the treatment, and 49.17 did not contract the virus with treatment. The P-Value:5.741e-06, is less than 0.05, so we reject the null hypothesis. The vaccine did have an effect on the LGBTQ community, but it was a negative effect because more LGBTQ contracted COVID-19 than not.