---
title: "Covid91 vaccine study Final2020"
author: "Arlene Faye Salvador"
date: "October 29, 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode aids to say covid and then remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine.

$H_0$ The Null Hypothesis is that among the target population, the vaccine has no effect on whether one contracts the virus or not.

$H_A$ The Alternative Hypothesis is that is that among the target population, the vaccine has an effect on whether one contracts the virus or not.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

# Graphical Results
# Female Report

```{r}
DataF = filter(FinalData, sex=="gal")
barchartGC(~infected + treatment,data=DataF)
barchartGC(~infected + treatment,data=DataF, type="percent")
```
It appears that the vaccine has a positive effect on the gals since they are less likely to get Covid-19 if they receive the vaccine.


```{r}
DataG = filter(FinalData, sex=="guy")
barchartGC(~infected + treatment,data=DataG)
barchartGC(~infected + treatment,data=DataG, type="percent")
```

It appears that the vaccine has a negative effect on the guys since they are more likely to get Covid-19 if they receive the vaccine.

